Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-03 PandaOverview.tex
Iteration 4 and scattered editing

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figures/panda_architecture.pdf}
  \end{center}
    \caption{PanDA architecture with the subsystems and components
    relevant to the integration of PanDA with supercomputers. Numbers indicates
    the execution process based on JEDI: From the submission of tasks (1) to the
    retrieval of their output (19). The monitoring subsystem, the architectural
    details of PanDA Pilot and the communication among subsystem's components
    are abstracted to improve clarity.}
\label{fig:architecture}
\end{figure}

@@

When a PanDA Pilot becomes available on a site, it calls the Job Dispatcher
module of the PanDA Server, requesting  a job to execute
(Fig.~\ref{fig:architecture}:11). The Job Dispatcher interrogates the Task
Buffer module for a job that is bound to the site of that pilot and ready to be
executed. Task Buffer checks the global queue (i.e., the PanDA database) and,
upon availability, returns a suitable job the Job Dispatcher. \jhanote{end of previous sentence needs some attention} The Job Dispatcher
dispatches that job to the PanDA Pilot (Fig.~\ref{fig:architecture}:12).

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/panda_architecture.pdf}
    \caption{PanDA architecture with the subsystems and components relevant to
    the integration of PanDA with supercomputers. Numbers indicates the
    execution process based on JEDI: From the submission of tasks (1) to the
    retrieval of their output (19). The monitoring subsystem, the architectural
    details of PanDA Pilot and the communication among subsystem's components
    are abstracted to improve clarity.}
\label{fig:architecture}
\end{figure}

@@

When a PanDA Pilot becomes available on a site, it calls the Job Dispatcher
module of the PanDA Server, requesting  a job to execute
(Fig.~\ref{fig:architecture}:11). The Job Dispatcher interrogates the Task
Buffer module for a job that is bound to the site of that pilot and ready to be
executed. Task Buffer checks the global queue (i.e., the PanDA database) and,
upon availability, returns a suitable job to the Job Dispatcher. \jhanote{end of
previous sentence needs some attention}\mtnote{Done.} The Job Dispatcher
dispatches that job to the PanDA Pilot (Fig.~\ref{fig:architecture}:12).
